Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli

### 2023-09-26 manuscript_draft.Rmd
fixing manuscript table issue

```{r table-scores-updated, results = 'asis', eval = F}
c_sample <- c(results_table_example$`C 80`[4], 
              results_table_example$`C 85`[4],
              results_table_example$`C 90`[4],
              results_table_example$`C 95`[4])

@@

apa_table(table_correction_applied, 
          caption = "Applied Correction for Each Proposed Sample Size", 
          font_size = "footnotesize")
```

>>>>

```{r table-scores-updated, results = 'asis', eval = T}
c_sample <- c(results_table_example$`C 80`[4], 
              results_table_example$`C 85`[4],
              results_table_example$`C 90`[4],
              results_table_example$`C 95`[4])

@@

apa_table(table_correction_applied, 
          caption = "Applied Correction for Each Proposed Sample Size", 
          font_size = "scriptsize", 
          landscape = TRUE)
```

### 2023-09-26 manuscript_draft.tex
fixing manuscript table issue

>>>>

\begin{lltable}

\scriptsize{

\begin{longtable}{llllllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:table-scores-updated}Applied Correction for Each Proposed Sample Size}\\
\toprule
Formula Estimate & \multicolumn{1}{c}{Intercept} & \multicolumn{1}{c}{Projected SS} & \multicolumn{1}{c}{Pilot SS} & \multicolumn{1}{c}{Log2 Projected SS} & \multicolumn{1}{c}{Log2 Pilot SS} & \multicolumn{1}{c}{Log2 Power} & \multicolumn{1}{c}{Prop Var} & \multicolumn{1}{c}{Log2 Prop Var} & \multicolumn{1}{c}{Power} & \multicolumn{1}{c}{Corrected Sample} & \multicolumn{1}{c}{Data Loss}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:table-scores-updated} continued}}\\
\toprule
Formula Estimate & \multicolumn{1}{c}{Intercept} & \multicolumn{1}{c}{Projected SS} & \multicolumn{1}{c}{Pilot SS} & \multicolumn{1}{c}{Log2 Projected SS} & \multicolumn{1}{c}{Log2 Pilot SS} & \multicolumn{1}{c}{Log2 Power} & \multicolumn{1}{c}{Prop Var} & \multicolumn{1}{c}{Log2 Prop Var} & \multicolumn{1}{c}{Power} & \multicolumn{1}{c}{Corrected Sample} & \multicolumn{1}{c}{Data Loss}\\
\midrule
\endhead
Formula & 206.59 & 0.37 & -0.77 & 27.54 & 2.58 & -66.15 & 16.40 & -1.37 & 1.09 & NA & NA\\
Concrete 80 & 1.00 & 45.00 & 28.00 & 5.49 & 4.81 & 6.32 & 0.13 & -2.94 & 80.00 & 40.25 & 44.84\\
Concrete 85 & 1.00 & 50.00 & 28.00 & 5.64 & 4.81 & 6.41 & 0.13 & -2.94 & 85.00 & 45.93 & 51.17\\
Concrete 90 & 1.00 & 50.00 & 28.00 & 5.64 & 4.81 & 6.49 & 0.13 & -2.94 & 90.00 & 45.92 & 51.15\\
Concrete 95 & 1.00 & 65.00 & 28.00 & 6.02 & 4.81 & 6.57 & 0.13 & -2.94 & 95.00 & 62.14 & 69.22\\
LDT 80 & 1.00 & 75.00 & 33.00 & 6.23 & 5.04 & 6.32 & 0.08 & -3.61 & 80.00 & 68.47 & 87.62\\
LDT 85 & 1.00 & 75.00 & 33.00 & 6.23 & 5.04 & 6.41 & 0.08 & -3.61 & 85.00 & 68.13 & 87.18\\
LDT 90 & 1.00 & 90.00 & 33.00 & 6.49 & 5.04 & 6.49 & 0.08 & -3.61 & 90.00 & 80.88 & 103.50\\
LDT 95 & 1.00 & 105.00 & 33.00 & 6.71 & 5.04 & 6.57 & 0.08 & -3.61 & 95.00 & 92.80 & 118.76\\
\bottomrule
\end{longtable}

\end{lltable}
